%-------------------------
% Resume in Latex
% Author : Rohit Midha
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubHeading}[2]{\textit{\small #1} \hfill \textit{\small #2} }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://rohitmidha23.github.io/}{\Large Rohit Midha}} & Email : \href{mailto:rohit.midha23@gmail.com}{rohit.midha23@gmail.com}\\
  \href{https://rohitmidha23.github.io/}{https://rohitmidha23.github.io/} & Mobile : +91 7358777008
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Tamil Nadu, India}
      {Bachelor of Engineering in Computer Science and Engineering;  GPA: 9.19/10.0}{Aug. 2017 -- July 2021}
     
      \small{University Rank: \#10, College Rank: \#3}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Goldman Sachs}{}
    {Engineering Analyst}{August 2021 -- Present}
    \resumeItemListStart
    \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
        \item By automating archaic workflows, RARE lowers costs and improves quality and UX of the review process, thus bringing transparency and effectiveness to a critical risk process.
        \item Reduced review time by a third, from over 6 hours to 2 hours.
        \item Engineered the backend artchitecture for the platform using  Java micro-services and deployed via Kubernetes.
        \item Designed the Stats and Management Dashboard to provide high level insights to senior management.
        \item Streamlined the data flow for calculating a key financial metric and spearheaded the initiative to on-board onto Snowflake. 
        \item Defined SLA and SLOs for our team's offerings using Prometheus for monitoring the Kubernetes deployments.
        \item Mentored and trained 3 graduate level software interns, with each getting return offers. 
        \item Awards: Runner Up, Innovation, Goldman Sachs Awards 2021 and Runner Up, Digital Poster, Goldman Sachs Internal Engineering Conference
      \end{itemize}
        }
    \resumeItemListEnd
    
    \resumeSubSubHeading {Summer Analyst}{May 2020 -- June 2020}
    \resumeItemListStart
    \resumeItem{Risk Metrics Inventory UI}
        {
          \begin{itemize}
          \item Developed a React UI that acts as a central registry and lets users perform CRUD operations on metrics meta-data, keeping inter-dependencies consistent.
          \item Reduced onboarding time from over 5 minutes to under a minute.
          \end{itemize}
        }
    \resumeItemListEnd

    \resumeSubheading
      {CodeFemme}{}
      {Founder, CTO}{June 2018 -- Present}
      \resumeItemListStart
      \resumeItem{Partner Schools}
          {Partnered with over 70 schools in the city to provide best in class Python workshops and class material for high school students.}
        \resumeItem{Te(a)chTheTeach}
          {Taught undergraduate level Python and important libraries to 100+ CBSE teachers through a workshop series aimed at teaching Post Graduate Teachers (PGTs).}
        \resumeItem{Numpy, Pandas and Neural Nets}
          {Guest Lecture on the topic "Numpy, Pandas and Neural Nets" at Kendra Vidyalya, Indian Institute of Technology, Madras. 50+ teachers from across the country in attendance.}
      \resumeItemListEnd

    \resumeSubheading
      {AIcrowd}{}
      {Research Intern}{March 2020 -- May 2020}
      \resumeItemListStart
      \resumeItem{World Health Organization}
        {Implemented Recognition models to identify various types of endangered snail species in the wild.}
      \resumeItem{AIcrowd Blitz}
        {Launched the Blitz series of challenges on the platform, curating datasets and defining tasks.}
    \resumeItemListEnd

    \resumeSubheading
    {Indian Institute of Technology, Madras}{}
    {Research Intern}{November 2019 -- May 2020}
    \resumeItemListStart
    \resumeItem{Mentors}
        {Professor Gitakrishnan Ramadurai, Professor Balaraman Ravindran}
      \resumeItem{Traffic Optimisation}
        {Developed a real-time Computer Vision based system, deployed to city wide CCTV cameras to optimise traffic lights based on predicted traffic.}
    \resumeItemListEnd
    
   \resumeSubheading
    {Sigmoid}{}
    {Data Scientist Intern}{May 2019 -- July 2019}
    \resumeItemListStart
      \resumeItem{Named Entity Recognition}
        {Remodeled Conditional Random Fields, Recurrent Neural Networks and Long Short Term Memories for Named Entity Recognition of Medical Drugs. Increased accuracy from 77\% to 81\%.}
\iffalse
        \resumeItem{Quantum Machine Learning}
        {Programmed QML algorithms using Variational Circuits for Credit Card Fraud Detection.}
\fi
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------Research and Publications--------
\section{Research: Posters, Publications and Talks}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\href{https://bit.ly/OpenImagesPoster2019}{A Low Cost Solution to the Open Images Instance Segmentation Challenge}}{Poster accepted at International Conference on Computer Vision (ICCV), 2019. \href{https://bit.ly/OpenImagesPoster2019}{Poster here.}}
       \resumeSubItem
      {\href{https://bit.ly/AMLDPresentationDEEP}{Transfer Learning for International Crisis Response}}{Talk and Presentation at the Challenge Track of Applied Machine Learning Days (AMLD), 2020 \href{https://bit.ly/AMLDPresentationDEEP}{Slides here.} }
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects and Ventures}
 \resumeSubHeadingListStart
  	\resumeSubItem{\href{https://bit.ly/PharmAssistDemo}{pharmAssist by That Medical Company}}
      {A novel label and Android App that lets visually impaired people gain health literacy. Reads out easy instructions for pills when prescription bottle is placed on phone screen. Connected with Alexa for easy access. \href{https://bit.ly/PharmAssistDemo}{Video demo here.}}
    \resumeSubItem{jargone}
      {A web app that summarizes Terms and Conditions to keep you informed about the data companies collect from you.}
      
    \resumeSubItem{Federated Learning for Medical Imaging}
      {A framework that provides a complete machine learning pipeline to let researchers and end users train any model on medical image data from various sources. Uses YAML files for simple configuration.}
  
    \resumeSubItem{Facial Recognition Attendance Manager}
      {Creating a prototype of a model attendance manager using Facial Recognition integrated with Raspberry Pi, Cameras and Firebase requests made by the student. \\Fully funded by SSN College of Engineering.}
\iffalse
    \resumeSubItem{Calmity}
      {An app that helps victims of a disaster find food, transport and shelter in nearby places and allows them to make SOS calls. Further, allows able users to finding NGOs that they can volunteer at and post about any amenities that they have to offer.}
    \resumeSubItem{trashify}
      {Android Application that uses Deep Learning and TensorFlowLite to classify your trash into 3 categories.\\Prototype of model using Raspberry Pi in implementation phase.}
\fi
    \resumeSubItem{Other}
      {The SSNMUN Website, binarify (convert images to binary art.)}
  \resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
  \resumeSubHeadingListStart
  \resumeSubItem
    {Runner Up, Goldman Sachs Hackathon}{2022}
  \resumeSubItem
    {Rank 2, Hockey Team Classification Challenge, AIcrowd}{October 2020}
  \resumeSubItem
    {Rank 2, Transfer Learning for International Crisis Response, DEEP}{Jan 2020}
  \resumeSubItem
    {Winner, AstraZeneca AI Hackathon}{Jan 2020}
  \resumeSubItem
    {Best Novice Speaker, Independent University Bangaldesh - Parlimentary Debate}{Dec 2019}
  \resumeSubItem
    {Rank 1, Round 1 - 3, Food Recognition Challenge, Seerave Foundation}{Dec 2019}
  \resumeSubItem
    {Rank 34, Open Images Instance Segmentation Challenge}{October 2019}
  \resumeSubItem
    {Runner Up, Amazon Web Services (AWS) Challenge, AngelHack Global Virtual Hackathon}{July 2019}
  \resumeSubItem
    {Winner, Indian Sub-Continent, AngelHack Global Virtual Hackathon}{July 2019}
  \resumeSubItem
    {Finalist, International Youth Math Challenge}{Nov 2018}

  \resumeSubHeadingListEnd
%--------Scholarships------------
\section{Scholarships}
  \resumeSubHeadingListStart
    \resumeSubItem
  {Rank 1, Merit Scholarship, SSN College of Engineering}{2019-20}
      \resumeSubItem
  {Merit Scholarship, SSN College of Engineering}{2017-18}
\resumeSubHeadingListEnd

%--------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C,  SQL, Java, JavaScript, HTML}
      }
      \item{
       \textbf{Frameworks and Technologies}{: React, Redux, NodeJS, Kubernetes, Prometheus, PyTorch, FastAI}
    }
  \resumeSubHeadingListEnd

\section{Volunteering}
\resumeSubHeadingListStart
\resumeItem{Google}{Organized the Google AI Explore ML Workshop at SSN College of Engineering.}
\resumeItem{Stanford University}{Section Leader for CS106A, offered during COVID-19 pandemic, with 10,000 global students participating from around the world.}
\resumeSubHeadingListEnd
%-------------------------------------------
%--------Blog------------
\iffalse
\section{Blog}
I also run a blog which you can find at \href{https://rohitmidha23.github.io/blog}{rohitmidha23.github.io/blog}. It has had over 30k page views.
\fi

\end{document}

