%-------------------------
% Resume in Latex
% Author : Rohit Midha
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubHeading}[2]{\textit{\small #1} \hfill \textit{\small #2} }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://rohitmidha23.github.io/}{\Large Rohit Midha}} & Email : \href{mailto:rohit.midha23@gmail.com}{rohit.midha23@gmail.com}\\
  \href{https://rohitmidha23.github.io/}{https://rohitmidha23.github.io/} & Mobile : +91 7358777008 \\
  {} & \href{https://github.com/RohitMidha23}{Github: RohitMidha23}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Tamil Nadu, India}
      {Bachelor of Engineering in Computer Science and Engineering;  GPA: 9.2/10.0}{Aug. 2017 -- July 2021}
      
      \small{University Rank: \#10, College Rank: \#3}
      \iffalse
    \resumeSubheading
      {Maharish Vidya Mandir Senior Secondary School}{Chennai, India}
      {High School Diploma;   AISSCE : 96.4\% (482/500)}{June. 2015 -- July. 2017}
      \fi
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Goldman Sachs}{}
    {Engineering Analyst}{August 2021 -- Present}
    \resumeItemListStart
    \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
        \item By automating archaic workflows, RARE lowers costs and improves quality and UX of the review process, thus bringing transparency and effectiveness to a critical risk process.
        \item Reduced Review time by a third, from over 6 hours to 2 hours.
        \item Introduced RARE Lite in an effort to acquire users who needed only a partial suite of services offered by the platform.       
        \item Introduced the Management Dashboard to provide high level insights to senior management, based on meta-data collected by the platform.
        \item Developed streaming data pipeline to push data to Snowflake using Apache Kafka and Alloy, a proprietary GS software.
        \item Streamlined the data flow for calculating a key financial metric reported and spearheaded the initiative to on-board onto Snowflake. 
        \item Defined SLA for our team's offerings using Prometheus for monitoring our Kubernetes deployments.
        \item Setup Grafana Dashboards to visualise some of our SLOs as well as Application Health page to monitor microservices.
        \item Developed APIs (Jackson, Java) for CRUD operations as well as for certain UI use-cases.
        \end{itemize}
        }
    \resumeItemListEnd

    \resumeSubSubHeading{Engineering Intern}{Jan 2021-- July 2021}
    \resumeItemListStart
    	\resumeItem{Risk Metric Model}
        {Developed the system architecture for scaling the system. Upgraded the backend to use Java with a Dropwizard server connected to Sybase ASE DB.}
        \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
        \item Shadowed users and documented user stories which helped in creating the initial requirements document.
        \item Developed the data model following microservice architecture, defining 3 services run on Java, Dropwizard backend. 
        \item Set up Kubernetes deployments for services with appropriate caching methodologies. 
        \item Introduced APIs for simplifying complex graph operations that represented Standard Business Hierarchy graphs for deliverables onboarded.
        \end{itemize}
        }
    \resumeItemListEnd
    
    \resumeSubSubHeading {Summer Analyst}{May 2020 -- June 2020}
    \resumeItemListStart
    \resumeItem{Risk Metrics Inventory UI}
        {Introduced a UI that acts as a central registry and lets users perform CRUD operations on metrics meta-data, keeping inter-dependencies consistent. Used modular design for components to generate them based on configuration files. Made with React and Redux. }
    \resumeItemListEnd

    \resumeSubheading
      {CodeFemme}{Chennai, India}
      {Founder, CTO}{June 2018 -- Present}
      \resumeItemListStart
      \resumeItem{Partner Schools}
          {Partnered with over 70 schools in the city to provide best in class Python workshops and class material for high school students.}
        \resumeItem{Te(a)chTheTeach}
          {Te(a)chTheTeach is a workshop series aimed at teaching PGT's about Python and it's various Libraries. Taught 100+ CBSE teachers so far.}
        \resumeItem{Numpy, Pandas and Neural Nets}
          {Guest Lecture on the topic "Numpy, Pandas and Neural Nets" at Kendra Vidyalya, Indian Institute of Technology, Madras. 50+ teachers from across the country in attendance.}
      \resumeItemListEnd

     \resumeSubheading
    {AIcrowd}{}
    {Research Intern}{March 2020 -- September 2020}
    \resumeItemListStart
    \resumeItem{World Health Organization}
        {Implemented Recognition models to identify various types of endangered snail species in the wild.}
    \resumeItem{AIcrowd Blitz}
        {Curated datasets and created baselines for the Mask Recognition Challenge, Food Classification Challenge and Scrambled Text Challenge.}
        \resumeItem{Food Recognition Challenge}
        {Challenge Organizer for Round 3 of the challenge. Created baselines using mmdetection for Round 3.}
    \resumeItemListEnd

    \resumeSubheading
    {Indian Institute of Technology, Madras}{Chennai, India}
    {Research Intern}{November 2019 -- May 2020}
    \resumeItemListStart
    \resumeItem{Mentors}
        {Professor Gitakrishnan Ramadurai, Professor Balaraman Ravindran}
      \resumeItem{License Plate Recognition}
        {Working on a system to recognise license plates from videos obtained from CCTV cameras.}
        \resumeItem{Vehicle Counting}
        {Developed a real time system that works with large scale data obtained from traffic cameras across the city for vehicle counting to model dynamic traffic flow.}
    \resumeItemListEnd
    
   \resumeSubheading
    {Sigmoid}{Bangalore, India}
    {Data Scientist Intern}{May 2019 -- July 2019}
        \resumeItemListStart
      \resumeItem{Named Entity Recognition}
        {Worked on using Conditional Random Fields, Recurrent Neural Networks and Long Short Term Memories for Named Entity Recognition of Medical Drugs. Increased accuracy from 77\% to 81\%.}
        \resumeItem{Quantum Machine Learning}
        {Wrote machine learning algorithms optimized to work on a quantum computer such as quantum linear regression and built a quantum Neural Network for Credit Card Fraud Detection.}
\iffalse
        \resumeItem{Quantum Neural Networks}
        {Implemented a Quantum Neural Network as a Variational Circuit for real world applications such as Credit Card Fraud Detection.}
\fi
    \resumeItemListEnd
\iffalse
  \resumeSubheading
    {SSN Model United Nations}{Chennai, India}
    {Under Secretary General, Technology and Development}{Apr 2019 -- Present}
        \resumeItemListStart
      \resumeItem{Team}
        {Heading a team of 5 developers in all matters Tech related for the college Model United Nations.}
        \resumeItem{Website}
        {Built a dynamic website with Python, Flask, HTML and JavaScript using basic concepts of Bootstrap and MongoDB. }
    \resumeItemListEnd
\fi
\resumeSubHeadingListEnd

%--------Research and Publications--------
\section{Research: Posters, Publications and Talks}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\href{https://bit.ly/OpenImagesPoster2019}{A Low Cost Solution to the Open Images Instance Segmentation Challenge}}{Poster accepted at International Conference on Computer Vision (ICCV), 2019. \href{https://bit.ly/OpenImagesPoster2019}{Poster here.}}
       \resumeSubItem
      {\href{https://bit.ly/AMLDPresentationDEEP}{Transfer Learning for International Crisis Response}}{Talk and Presentation at the Challenge Track of Applied Machine Learning Days (AMLD), 2020 \href{https://bit.ly/AMLDPresentationDEEP}{Slides here.} }
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
 \resumeSubHeadingListStart
  	\resumeSubItem{\href{https://bit.ly/PharmAssistDemo}{pharmassist}}
      {A novel label and Android App that lets visually impaired people gain health literacy. Reads out easy instructions for pills when prescription bottle is placed on phone screen. Connected with Alexa for easy access. \href{https://bit.ly/PharmAssistDemo}{Video demo here.}}
  \resumeSubItem{jargone}
      {A web app that summarizes Terms and Conditions to keep you informed about the data companies collect from you.}
      
      \resumeSubItem{Federated Learning for Medical Imaging}
      {A framework that provides a complete machine learning pipeline to let researchers and end users train any model on medical image data from various sources. Uses YAML files for simple configuration.}
  
    \resumeSubItem{Facial Recognition Attendance Manager}
      {Creating a prototype of a model attendance manager using Facial Recognition integrated with Raspberry Pi, Cameras and Firebase requests made by the student. \\Fully funded by SSN College of Engineering.}
      \iffalse
    \resumeSubItem{Calmity}
      {An app that helps victims of a disaster find food, transport and shelter in nearby places and allows them to make SOS calls. Further, allows able users to finding NGOs that they can volunteer at and post about any amenities that they have to offer.}
      \resumeSubItem{trashify}
      {Android Application that uses Deep Learning and TensorFlowLite to classify your trash into 3 categories.\\Prototype of model using Raspberry Pi in implementation phase.}
\fi
      \resumeSubItem{Other}
      {The SSNMUN Website, binarify (convert images to binary art.)}
  \resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
  \resumeSubHeadingListStart
   \resumeSubItem
  {Runner Up, Goldman Sachs Hackathon}{2022}
   \resumeSubItem
  {Runner Up, Digital Poster, Goldman Sachs Internal Engineering Conference}{2022}
  \resumeSubItem
  {Runner Up, Innovation, Goldman Sachs Awards}{2021}
   \resumeSubItem
  {Rank 2, Hockey Team Classification Challenge, AIcrowd}{October 2020}
   \resumeSubItem
  {Rank 2, Transfer Learning for International Crisis Response, DEEP - AIcrowd}{Jan 2020}
   \resumeSubItem
  {Winner, AstraZeneca AI Hackathon, IIT Madras}{Jan 2020}
  \resumeSubItem
  {Rank 1, Round 1 - 3, Food Recognition Challenge, Seerave Foundation}{Dec 2019}
  \resumeSubItem
  {Rank 34, Open Images Instance Segmentation Challenge}{October 2019}
       \resumeSubItem
  {Runner Up, Amazon Web Services (AWS) Challenge, AngelHack Global Virtual Hackathon}{July 2019}
     \resumeSubItem
  {Winner, Indian Sub-Continent, AngelHack Global Virtual Hackathon}{July 2019}
   \resumeSubItem
  {Rank 208 of 6000+ participants, IEEE CIS Fraud Detection Challenge}{October 2019}
  \resumeSubItem
  {Rank 503 of 9000+ participants, Santander Customer Transaction Prediction }{April 2019}
    \resumeSubItem
  {Runner Up, MotorQ Hackathon}{March 2019}
     \resumeSubItem
      {Top 5 Teams, Major League Hacking, Local Hack Day}{Dec 2018}
  \resumeSubItem
    {Finalist, International Youth Math Challenge}{Nov 2018}
\iffalse
    \resumeSubItem
      {Indumathi Muthukumar Award}{June 2017}
\fi
  \resumeSubHeadingListEnd
%--------Scholarships------------
\section{Scholarships}
  \resumeSubHeadingListStart
    \resumeSubItem
  {Rank 1, Merit Scholarship, SSN College of Engineering}{2019-20}
      \resumeSubItem
  {Merit Scholarship, SSN College of Engineering}{2017-18}
\resumeSubHeadingListEnd

%-------------------------------------------
%--------Certifications------------
\iffalse
\section{Certifications}
  \resumeSubHeadingListStart
        \resumeSubItem
  {Natural Language Processing with Tensorflow, deeplearning.ai}{July 2019}
        \resumeSubItem
  {Neural Networks and Deep Learning, deeplearning.ai (Scholarship)}{Mar 2019}
      \resumeSubItem
  {Introduction to TensorFlow for AI, ML and DL, deeplearning.ai (Scholarship)}{Mar 2019}
    \resumeSubItem
      {Data Science Foundations - Level 2, IBM}{Jan 2019}
    \resumeSubItem
  {Machine Learning, Stanford University (Scholarship)}{Apr 2018}
    \resumeSubItem
  {Introduction to Mathematical Thinking, Stanford University (Scholarship)}{Jan 2018} 	
\resumeSubHeadingListEnd
\fi

%--------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C,  SQL, Java, JavaScript, HTML}
      }
      \item{
       \textbf{Frameworks and Technologies}{: React, Redux, NodeJS, Kubernetes, Prometheus, PyTorch, FastAI}
    }
  \resumeSubHeadingListEnd

\section{Volunteering}
\resumeSubHeadingListStart
\resumeItem{Google}{Organized the Google AI Explore ML Workshop at SSN College of Engineering.}
\resumeItem{Stanford University}{Section Leader for CS106A, offered during COVID-19 pandemic, with 10,000 global students participating from around the world.}
\resumeSubHeadingListEnd
%-------------------------------------------
%--------Blog------------
\iffalse
\section{Blog}
I also run a blog which you can find at \href{https://rohitmidha23.github.io/blog}{rohitmidha23.github.io/blog}. It has had over 30k page views.
\fi

\end{document}

