%-------------------------
% Resume in Latex
% Author : Rohit Midha
% License : MIT
%------------------------

% This resume is for Full Stack / SDE Jobs only. 

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubHeading}[2]{\textit{\small #1} \hfill \textit{\small #2} }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Rohit Midha} & Email: \href{mailto:rohit.midha23@gmail.com}{rohit.midha23@gmail.com}\\
  \href{https://rohitmidha23.github.io/}{https://rohitmidha23.github.io/} & Mobile: +44 7444 651443 \\
  {} & \href{https://github.com/RohitMidha23}{Github: RohitMidha23}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, United Kingdom}
      {MSc Computing (Artificial Intelligence and Machine Learning)}{Sept. 2023 -- Sept. 2024}
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Tamil Nadu, India}
      {Bachelor of Engineering in Computer Science and Engineering;  \textbf{GPA: 9.2/10}}{Aug. 2017 -- July 2021}
      
      \small{University Rank: \#10, College Rank: \#3}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {\href{https://www.srmd.org/en-GB/}{Shrimad Rajchandra Mission, Dharampur}}{}
  {AI Engineer}{December 2022 -- Present }
    \resumeItemListStart
      \resumeItem{\href{https://www.srmd.org/en-GB/news/shrimad-rajchandra-mission-dharampur-introduces-a-pathbreaking-initiative-artificial-intelligence-makes-spirituality-accessible-globally/}{Multilingual AI}}
      {Engineered personalized text-to-speech synthesis models across eight languages, embodying Gurudev's unique vocal essence, thereby broadening access to spiritual wisdom. \href{https://www.instagram.com/reel/CxI8gwcohG5/}{View Global Launch!} 
      }
      \resumeItem{Audience Quiz}{
        \begin{itemize}
          \item Designed and implemented a highly scalable quiz application with NextJS + TailwindCSS, seamlessly accommodating an expansive user base of over 10,000 concurrent participants. 
          \item Optimized performance in a resource-constrained ecosystem characterized by a 512kbps internet connection and a singular 8GB quad-core Dell server. 
        \end{itemize}
        }
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.goldmansachs.com/}{Goldman Sachs}}{}
    {Engineering Analyst}{August 2021 -- May 2023}
    \resumeItemListStart
    \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
          \item By automating archaic workflows, RARE lowers costs and improves the quality and UX of the review process.
          \item Reduced review time by a third, from over 6 hours to under 2 hours.
          \item Engineered the backend architecture for the platform using  Java micro-services and deployed via Kubernetes.
          \item Designed the Stats and Management Dashboard to provide high-level insights to senior management.
          \item Optimized data flow for calculating key metrics like Net Cash Outflow across various business hierarchies.
          \item Spearheaded the initiative to onboard onto Snowflake, reducing data access time by 41\%. 
          \item Defined the SLA and set up a custom Prometheus framework for monitoring the Kubernetes deployments.
          \item \textbf{Awards}: Runner Up, Innovation, Goldman Sachs Awards 2021 and Runner Up, Digital Poster, Goldman Sachs Internal Engineering Conference
        \end{itemize}
        }
    \resumeItemListEnd
\iffalse
    \resumeSubheading
    {Indian Institute of Technology, Madras}{Chennai, India}
    {Research Intern}{November 2019 -- May 2020}
    \resumeItemListStart
    \resumeItem{Mentors}
        {Professor Gitakrishnan Ramadurai, Professor Balaraman Ravindran}
      \resumeItem{Traffic Optimisation}
      {
        \begin{itemize}
        \item Developed software integrated across state-wide CCTV camera networks to intelligently optimize traffic signal operations through predictive traffic analysis. 
        \item Implemented vision models capable of accurately identifying license plates for vehicles that contravene traffic regulations, achieving a remarkable precision rate of 86\%.
        \end{itemize}
		  }

    \resumeItemListEnd
\fi
\resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
  \resumeSubHeadingListStart
   \resumeSubItem
  {Runner Up, Goldman Sachs Hackathon}{2022}
   \resumeSubItem
  {\href{https://bit.ly/AMLDPresentationDEEP}{Rank 2, Transfer Learning for International Crisis Response}, DEEP - AIcrowd}{Jan 2020}
    \resumeSubItem
  {Merit Scholarship, SSN College of Engineering}{2017-18, 2019-20}
  \resumeSubItem
  {\href{https://www.aicrowd.com/challenges/food-recognition-challenge/leaderboards?challenge_round_id=116}{Rank 1, Round 1 - 3, Food Recognition Challenge}, Seerave Foundation}{Dec 2019}
     \resumeSubItem
  {Winner, Indian Sub-Continent, AngelHack Global Virtual Hackathon}{July 2019}
  \resumeSubHeadingListEnd


%--------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C,  SQL, Java, JavaScript, HTML, CSS}
      }
      \item{
       \textbf{Frameworks and Technologies}{: React, NodeJS, Kubernetes, Docker, PyTorch, GCP, AWS, Replicate, TailwindCSS, NextJS}
    }
  \resumeSubHeadingListEnd

\section{Volunteering}
\resumeSubHeadingListStart
\resumeItem{\href{https://codefemme.github.io/}{CodeFemme}}{Partnered with over 70 schools in the city to provide best-in-class Python workshops for teachers and class material for high school students.}
\resumeItem{Google}{Organized the Google AI Explore ML Workshop at SSN College of Engineering.}
\resumeItem{Stanford University}{Section Leader for \href{https://codeinplace.stanford.edu/}{CS106A - Code in Place}, offered during COVID-19 pandemic, with 10,000 global students participating from around the world.}
\resumeSubHeadingListEnd


\end{document}

