%-------------------------
% Resume in Latex
% Author: Rohit Midha
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubHeading}[2]{\textit{\small #1} \hfill \textit{\small #2} }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Rohit Midha} & Email: \href{mailto:rohit.midha23@gmail.com}{rohit.midha23@gmail.com}\\
  \href{https://rohitmidha23.github.io/}{https://rohitmidha23.github.io/} & Mobile: +44 7444 651443 \\
  {} & \href{https://github.com/RohitMidha23}{Github: RohitMidha23}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, United Kingdom}
      {MSc Computing (Artificial Intelligence and Machine Learning)}{Sept. 2023 -- Sept. 2024}
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Tamil Nadu, India}
      {Bachelor of Engineering in Computer Science and Engineering;  \textbf{GPA: 9.2/10}}{Aug. 2017 -- July 2021}
      
      \small{University Rank: \#10, College Rank: \#3}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {\href{https://www.srmd.org/en-GB/}{Shrimad Rajchandra Mission, Dharampur}}{}
  {AI Engineer}{December 2022 -- Present }
    \resumeItemListStart
    \resumeItem{\href{https://www.srmd.org/en-GB/news/shrimad-rajchandra-mission-dharampur-introduces-a-pathbreaking-initiative-artificial-intelligence-makes-spirituality-accessible-globally/}{Multilingual AI}}
      {
        \begin{itemize}
          \item Engineered personalized text-to-speech synthesis models across eight languages, embodying Gurudev's unique vocal essence, thereby broadening access to spiritual wisdom. \href{https://www.instagram.com/reel/CxI8gwcohG5/}{View Global Launch!} 
          \item Implemented Speech to Translated Text (S2TT) and Automatic Speech Recognition (ASR) pipelines to automate subtitling and translation processes for various low resource Indian languges.
        \end{itemize}
      }  
    \resumeItemListEnd

    \resumeSubheading
  {Langchain}{}
  {Open Source Contributor}{May 2023 -- Present}
    \resumeItemListStart
      \resumeItem{LangchainJS}
      {
        \begin{itemize}
          \item Implemented various LLM chains, such as the Refine LLM Chain for long form documents.
          \item Introduced Entity Memory store in that interacts with LLM Chains and Prompt Templates to provide entity context. 
        \end{itemize}
      }  
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.goldmansachs.com/}{Goldman Sachs}}{}
    {Engineering Analyst}{August 2021 -- May 2023}
    \resumeItemListStart
    \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
        \item By automating archaic workflows, RARE lowers costs and improves the quality and UX of the review process.
        \item Designed backend architecure for early detection of anomalies, increasing anomaly detection by 30\%.
        \item Designed the Stats and Management Dashboard to provide high-level insights to senior management.
        \item Mentored and trained 5 graduate-level software developer new hires. 
        \end{itemize}
        }
    \resumeItemListEnd

\resumeSubHeadingListEnd

%--------Research and Publications--------
\section{Research: Posters, Publications and Talks}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\href{https://bit.ly/OpenImagesPoster2019}{A Low-Cost Solution to the Open Images Instance Segmentation Challenge}}{Poster accepted at International Conference on Computer Vision (ICCV), 2019. \href{https://bit.ly/OpenImagesPoster2019}{Poster here.}}
    \resumeSubItem
      {\href{https://bit.ly/AMLDPresentationDEEP}{Transfer Learning for International Crisis Response}}{Talk and Presentation at the Challenge Track of Applied Machine Learning Days (AMLD), 2020. \href{https://bit.ly/AMLDPresentationDEEP}{Slides here.} }
  \resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
  \resumeSubHeadingListStart
  \resumeSubItem
    {Runner Up, Goldman Sachs Hackathon}{2022}
  
  \resumeSubItem
    {\href{https://bit.ly/AMLDPresentationDEEP}{Rank 2, Transfer Learning for International Crisis Response}, DEEP - AIcrowd}{Jan 2020}
  \resumeSubItem
  {Merit Scholarship, SSN College of Engineering}{2017-18, 2019-20}
  \resumeSubItem
    {Winner, AstraZeneca AI Hackathon}{Jan 2020}

  \resumeSubHeadingListEnd


%--------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, SQL, Java, JavaScript, HTML, CSS}
      }
      \item{
       \textbf{Frameworks and Technologies}{: React, NodeJS, Kubernetes, Docker, PyTorch, Langchain, HuggingFace, GCP, AWS, Replicate, TailwindCSS, NextJS}
    }
  \resumeSubHeadingListEnd


\end{document}