%-------------------------
% Resume in Latex
% Author: Rohit Midha
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.3in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubSubHeading}[2]{\textit{\small #1} \hfill \textit{\small #2} }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Rohit Midha} & Email: \href{mailto:rohit.midha23@gmail.com}{rohit.midha23@gmail.com}\\
  \href{https://rohitmidha23.github.io/}{https://rohitmidha23.github.io/} & Mobile: +44 7444 651443 \\
  {} & \href{https://github.com/RohitMidha23}{Github: RohitMidha23}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, United Kingdom}
      {MSc Computing (Artificial Intelligence and Machine Learning)}{Sept. 2023 -- Sept. 2024}
\iffalse
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Tamil Nadu, India}
      {Bachelor of Engineering in Computer Science and Engineering;  \textbf{GPA: 9.2/10}}{Aug. 2017 -- July 2021}
      
      \small{University Rank: \#10, College Rank: \#3}
\fi
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {\href{https://www.srmd.org/en-GB/}{Shrimad Rajchandra Mission, Dharampur}}{}
  {AI Engineer Volunteer}{December 2022 -- Present }
    \resumeItemListStart
    \resumeItem{\href{https://www.srmd.org/en-GB/news/shrimad-rajchandra-mission-dharampur-introduces-a-pathbreaking-initiative-artificial-intelligence-makes-spirituality-accessible-globally/}{Multilingual AI}}
    {Engineered personalized text-to-speech synthesis models across eight languages, embodying Gurudev's unique vocal essence, thereby broadening access to spiritual wisdom. \href{https://www.instagram.com/reel/CxI8gwcohG5/}{View Global Launch!} 
    }
    \resumeItemListEnd


    \resumeSubheading
    {\href{https://www.goldmansachs.com/}{Goldman Sachs}}{}
    {Engineering Analyst}{August 2021 -- May 2023}
    \resumeItemListStart
    \resumeItem{Risk Analysis and Review Engine (RARE)}
        {
        \begin{itemize}
        \item By automating archaic workflows, RARE lowers costs and improves the quality and UX of the review process.
        \item Designed backend architecure for early detection of anomalies, increasing anomaly detection by 30\%.
        \item Designed the Stats and Management Dashboard to provide high-level insights to senior management.
        \item Mentored and trained 5 graduate-level software developer new hires. 
        \end{itemize}
        }
    \resumeItemListEnd
    \iffalse
    \resumeSubSubHeading {Summer Analyst}{May 2020 -- June 2020}
    \resumeItemListStart
    \resumeItem{Risk Metrics Inventory UI}
        {
          \begin{itemize}
          \item Developed a React UI that acts as a central registry and lets users perform CRUD operations on metrics meta-data, keeping inter-dependencies consistent.
          \item Reduced onboarding time from over 5 minutes to under a minute.
          \end{itemize}
        }
    \resumeItemListEnd
    \fi
    \resumeSubheading
    {Indian Institute of Technology, Madras}{}
    {Research Intern}{November 2019 -- May 2020}
    \resumeItemListStart
    \resumeItem{Mentors}
        {Professor Gitakrishnan Ramadurai, Professor Balaraman Ravindran}
        \resumeItem{Traffic Optimisation}
        {
          \begin{itemize}
          \item Developed software integrated across state-wide CCTV camera networks to intelligently optimize traffic signal operations through predictive traffic analysis. 
          \item Implemented vision models capable of accurately identifying license plates for vehicles that contravene traffic regulations, achieving a remarkable precision rate of 86\%.
          \end{itemize}
        }
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--------Research and Publications--------
\section{Research: Posters, Publications and Talks}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\href{https://bit.ly/OpenImagesPoster2019}{A Low-Cost Solution to the Open Images Instance Segmentation Challenge}}{Poster accepted at International Conference on Computer Vision (ICCV), 2019. \href{https://bit.ly/OpenImagesPoster2019}{Poster here.}}
    \resumeSubItem
      {\href{https://bit.ly/AMLDPresentationDEEP}{Transfer Learning for International Crisis Response}}{Talk and Presentation at the Challenge Track of Applied Machine Learning Days (AMLD), 2020. \href{https://bit.ly/AMLDPresentationDEEP}{Slides here.} }
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects and Ventures}
 \resumeSubHeadingListStart
  	\resumeSubItem{\href{https://bit.ly/PharmAssistDemo}{pharmAssist by That Medical Company}}
      {A novel label and Android App that lets visually impaired people gain health literacy. Reads out easy instructions for pills when the prescription bottle is placed on the phone screen. Connected with Alexa for easy access. \href{https://bit.ly/PharmAssistDemo}{Watch the demo!}}
      
    \resumeSubItem{\href{https://github.com/sainath24/federated_learning}{Federated Learning for Medical Imaging}}
      {A FL framework that provides a complete machine learning pipeline to let researchers and end users train any model on medical image data from various servers.}
  \resumeSubHeadingListEnd

%--------Achievements------------
\section{Achievements}
  \resumeSubHeadingListStart
  \resumeSubItem
    {Runner Up, Goldman Sachs Hackathon}{2022}
  \resumeSubItem
    {\href{https://www.aicrowd.com/challenges/hockey-team-classification/leaderboards}{Rank 2, Hockey Team Classification Challenge}, AIcrowd}{October 2020}

  \resumeSubItem
    {Winner, AstraZeneca AI Hackathon}{Jan 2020}
  \resumeSubItem
    {\href{https://www.aicrowd.com/challenges/food-recognition-challenge/leaderboards?challenge_round_id=116}{Rank 1, Round 1 - 3, Food Recognition Challenge}, Seerave Foundation}{Dec 2019}
  \resumeSubItem
  {Merit Scholarship, SSN College of Engineering}{2017-18, 2019-20}

  \resumeSubHeadingListEnd


%--------------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, SQL, Java, JavaScript, HTML, CSS}
      }
      \item{
       \textbf{Frameworks and Technologies}{: React, NodeJS, Kubernetes, Docker, PyTorch, Langchain, HuggingFace, GCP, AWS, Replicate, TailwindCSS, NextJS}
    }
  \resumeSubHeadingListEnd

\end{document}